Contextuality and the Born rule in fuzzy quantum theories

### 2017-05-10 prop_letter.tex
prop.bib Updated to fix our erratum with BibTeX with PRL...

Our first observation is that essential objectives of our program to achieve a computable theory of quantum mechanics and finite-resource measurement, attempted previously with computable number systems~\cite{usat,geometry2013,DQT2014}, may be achievable by extending classical interval-valued probability measures~\cite{JamisonLodwick2004} to the quantum domain.  We begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework exploiting the fact that a density matrix approach can be considered as equivalent to a description of quantum states using probability measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307 One result is that the expectation value of an observable with respect to a QIVPM can be defined to be consistent with the constraints on the expectation value of the same observable expected from continuous quantum mechanics.  We then examine Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the Kochen-Specker theorem in the context of QIVPM's, and conclude that they correspond to the limit of an infinite number of precise intervals, and the set of crypto-deterministic intervals (the set $\{\imposs,\necess\}$), respectively.

>>>>

Our first observation is that essential objectives of our program to achieve a
computable theory of quantum mechanics and finite-resource measurement,
attempted previously with computable number systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by extending classical interval-valued probability measures~\cite{JamisonLodwick2004} to the quantum domain.  We begin by axiomatizing a quantum interval-valued probability measure (QIVPM) framework exploiting the fact that a density matrix approach can be considered as equivalent to a description of quantum states using probability measures~\cite{10.2307/2308516,Varadarajan2008}. %Mackey=10.2307 One result is that the expectation value of an observable with respect to a QIVPM can be defined to be consistent with the constraints on the expectation value of the same observable expected from continuous quantum mechanics.  We then examine Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum} and the Kochen-Specker theorem in the context of QIVPM's, and conclude that they correspond to the limit of an infinite number of precise intervals, and the set of crypto-deterministic intervals (the set $\{\imposs,\necess\}$), respectively.
